---
output:
  pdf_document:
    toc: false
    includes:
       in_header: codecheck-preamble.sty
    latex_engine: xelatex
---

```{r rsetup,eval=TRUE,include=FALSE}
require("codecheck")
require("knitr")
require("rprojroot")
require("yaml")
require("xtable")
require("tibble")
require("readr")
options(width = 60)
opts_chunk$set(cache=FALSE)

root = find_root("codecheck.yml")
```

```{r codecheck_logo, echo=FALSE,results='asis'}
latex_codecheck_logo()
```

```{r manifest, eval=TRUE, include=FALSE}
metadata = codecheck_metadata(root)
manifest = metadata$manifest

dest_dir = file.path(root, "codecheck", "outputs")
## Create the outputs directory if missing
if ( !dir.exists(dest_dir) ) {
  dir.create(dest_dir, recursive = TRUE)
}

manifest_df = copy_manifest_files(root, metadata,
                                  dest_dir, keep_full_path = FALSE,
                                  overwrite = FALSE
                                  )
```

---
title: `r paste("CODECHECK certificate", metadata$certificate)`
subtitle: `r codecheck:::as_latex_url(metadata$report)`
---

```{r summary_metadata, echo=FALSE, results='asis'}
latex_summary_of_metadata(metadata)
```

```{r summary_manifest, echo=FALSE, results='asis'}
latex_summary_of_manifest(metadata, manifest_df, root)
```

# Summary

The article referenced data and code in a OSF project. 
An included computational notebook in R Markdown format could be executed without errors and Figure 1, Figure 2, Figure 3, and Table 2 as well as numerical statics could be recreated with the code in the notebook.
The data deposit contains further files matching other tables in the article, though these are likely, at least partially, manually created and out of scope.
The check was successful.

\clearpage

# CODECHECKER notes

```{r git_sha, echo=FALSE}
gitInfo <- ""
if(git2r::in_repository(root)) {
  gitInfo <- paste0("This check is based on the commit `", git2r::last_commit()$sha, "`.")
}
```

This check is based on a submission to the [Lifecycle Journal](https://lifecyclejournal.org/).
Basis for evaluation is the registration of the code and data repository linked from the article page at <https://doi.org/10.17605/OSF.IO/BMQCW> (the registration of the project linked in the article).
The used article was published in the Lifecycle Journal Apr 29, 2025 with "Version 1 | Status: Under Evaluation".
The **materials** of the article include data and code, both are published on OSF in the project <https://osf.io/jwcmu/>.
This check starts with the article in PDF form and the archive `data and code.zip` (<https://osf.io/pexfb>, from the registration).

The article does point to the OSF project several times, but there are no details or instructions.
The archive contains a `README.md` file, which however only includes the abstract and the license (CC-BY 4.0).
The archive contains three folders with several subfolders.
Here is the full file tree:

\footnotesize

```{r filetree, echo=FALSE}
fs::dir_tree("../data and code/", regexp = "*__MACOSX/*", invert = TRUE)
```

\normalsize

I did a manual matching of the files in the archive and the figures in the article due to a lack of documentation.

\footnotesize

| Article | File             | Visual/manual inspection, comment |
|:---|:---------------------|:------------|
| Figure 1 | `-`  | no corresponding file, but computational notebook section "Sensitivity analysis: Exclude Tjak et al. (2018)" creates a matching the figure |
| Table 1 | `data and code/data/processed/summary_statistics_comparisons.xlsx` | the same, though spreadsheet has extra highlights |
| Figure 2 | `data and code/communciations/plots/verification_zhao_2023_comparisons_plot.pdf/png` | the same |
| Table 2 | `data and code/data/raw/data_zhao_forest_plot_1_extracted.xlsx` | matches a combination of sheets "original" and "reextracted" |
| Table 3 | `-` | no corresponding file, matches the table in notebook section "Outlier/undue influence tests" |
| Figure 3 | `data and code/communciations/plots/new_meta.png` | also matches notebook section "Sensitivity analysis: Exclude Zemestani et al. (2020)", it is unclear why this is not also saved as a plot in the notebook |
| `-` | `data and code/data/processed/influence_recalculated.xlsx` | no matching table found |
| `-` | `data and code/data/processed/influence_zhao.xlsx` | no matching table found, but matches table generated in notebook section "Outlier/undue influence tests" |
| `-` | `data and code/communciations/plots/verification_zhao_2023_comparisons_plot_alt.pdf/png` | mo matching figure found |

\normalsize

I add the matching files to the manifest for this check (see `codecheck.yml`).
Next, I check out the computational notebook in `data and code/code/analysis/`, which is an R Markdown file, `verification_zhao_2023.Rmd` that is also provided in a rendered output file, `verification_zhao_2023.html`.
Based on the provided information, I expand the table above.

I continue with the `.Rmd` file, beginning with installing missing packages, which could be installed without any errors.
Here is the output of my `sessionInfo()` after successfully rendering the computational notebook using RStudio's "Knit"-button without any errors within a few moments on my laptop:

\tiny

```txt
R version 4.5.0 (2025-04-11)
Platform: x86_64-pc-linux-gnu
Running under: Ubuntu 22.04.5 LTS

Matrix products: default
BLAS:   /usr/lib/x86_64-linux-gnu/blas/libblas.so.3.10.0 
LAPACK: /usr/lib/x86_64-linux-gnu/lapack/liblapack.so.3.10.0  LAPACK version 3.10.0

locale:
 [1] LC_CTYPE=en_US.UTF-8       LC_NUMERIC=C               LC_TIME=de_DE.UTF-8        LC_COLLATE=en_US.UTF-8     LC_MONETARY=de_DE.UTF-8    LC_MESSAGES=en_US.UTF-8    LC_PAPER=de_DE.UTF-8      
 [8] LC_NAME=C                  LC_ADDRESS=C               LC_TELEPHONE=C             LC_MEASUREMENT=de_DE.UTF-8 LC_IDENTIFICATION=C       

time zone: Europe/Berlin
tzcode source: system (glibc)

attached base packages:
[1] stats     graphics  grDevices datasets  utils     methods   base     

other attached packages:
 [1] lubridate_1.9.4  forcats_1.0.0    stringr_1.5.1    dplyr_1.1.4      purrr_1.0.4      tidyr_1.3.1      ggplot2_3.5.2    tidyverse_2.0.0  readr_2.1.5      tibble_3.2.1     xtable_1.8-4    
[12] yaml_2.3.10      rprojroot_2.0.4  knitr_1.50       codecheck_0.14.0 parsedate_1.3.2  R.cache_0.16.0   gh_1.4.1        

loaded via a namespace (and not attached):
 [1] tidyselect_1.2.1  R.utils_2.13.0    fastmap_1.2.0     XML_3.99-0.18     digest_0.6.37     timechange_0.3.0  lifecycle_1.0.4   qpdf_1.3.5        magrittr_2.0.3    zen4R_0.10        compiler_4.5.0   
[12] rlang_1.1.6       sass_0.4.10       tools_4.5.0       utf8_1.2.4        fauxpas_0.5.2     askpass_1.2.1     bit_4.6.0         curl_6.2.2        plyr_1.8.9        xml2_1.3.8        pkgload_1.4.0    
[23] redland_1.0.17-18 httpcode_0.3.0    withr_3.0.2       rdflib_0.2.9      R.oo_1.27.0       grid_4.5.0        roxygen2_7.3.2    atom4R_0.3-3      rorcid_0.7.0      colorspace_2.1-1  scales_1.3.0     
[34] crul_1.5.0        cli_3.6.5         rmarkdown_2.29    crayon_1.5.3      generics_0.1.3    rstudioapi_0.17.1 httr_1.4.7        tzdb_0.5.0        dadjokeapi_1.0.2  cachem_1.1.0      assertthat_0.2.1 
[45] parallel_4.5.0    vctrs_0.6.5       jsonlite_2.0.0    hms_1.1.3         bit64_4.6.0-1     jquerylib_0.1.4   keyring_1.3.2     glue_1.8.0        stringi_1.8.7     gtable_0.3.6      munsell_0.5.1    
[56] bspm_0.5.7        pillar_1.10.2     htmltools_0.5.8.1 R6_2.6.1          vroom_1.6.5       evaluate_1.0.3    osfr_0.2.9        R.methodsS3_1.8.2 png_0.1-8         memoise_2.0.1     bslib_0.9.0      
[67] Rcpp_1.0.14       zip_2.3.2         whisker_0.4.1     xfun_0.52         fs_1.6.6          pdftools_3.5.0    pkgconfig_2.0.3  
```

\normalsize

Further statistics calculated in the computational notebook match statistical numbers in the article, though a precise check is out of scope for this evaluation due to missing documentation.

## Recommendations

I suggest to the authors to consider the following suggestions for their next publication or workflow:

- Use appropriate data and software licenses - CC-BY is not ideal for either.
- Use precise file names in your data export and expand README to make clear which file corresponds to which figure; all files should be saved through a code statement (not done for `new_meta.png`).
- Provide documentation or even snapshot of the used packages (`sessionInfo()`, `renv` project, ..).
- Very clearly mention in the article where in the computational notebook statistics are calculated.
- Reference the registration in your article, ideally as a proper citation.

\clearpage

# Manifest files

```{r manifest-files, echo=FALSE, results="asis", width=100}
for(i in c(1:nrow(manifest_df))) {
  path <- manifest_df[i,"dest"]
  if(stringr::str_ends(path, "(png|pdf|jpg|jpeg)")) {
    # include graphics with knitr has to happen at top level in chunks, see https://github.com/yihui/knitr/issues/1260
    # see also https://stackoverflow.com/questions/51268623/insert-images-using-knitrinclude-graphics-in-a-for-loop
    # knitr::include_graphics(manifest_df[1, "dest"], error = TRUE)
    # Therefore, generate Markdown code here:
    cat("## ", basename(path), "\n\n")
    cat("**Comment:** ", manifest_df[i,"comment"], "\n\n")
    cat(paste0("![", "Test ", "](", path, ")\n"))
  } else if (stringr::str_ends(path, "(Rout|txt)")) {
    cat("## ", basename(path), "\n\n")
    cat("\\scriptsize \n\n", "```txt\n")
    cat(readLines(path), sep = "\n")
    cat("\n\n``` \n\n", "\\normalsize \n\n")
  } else if (stringr::str_ends(path, "csv")) {
    cat("## ", basename(path), "\n\n", "Summary statistics of tabular data:", "\n\n")
    cat("\\scriptsize \n\n", "```txt\n")
    print(skimr::skim(read.csv(path)))
    cat("\n\n``` \n\n", "\\normalsize \n\n")
  } else if (stringr::str_ends(path, "(xls|xlsx)")) {
    cat("## ", basename(path), "\n\n", "Partial content of tabular data:", "\n\n")
    cat("\\scriptsize \n\n", "```txt\n")
    print(readxl::read_excel(path))
    cat("\n\n``` \n\n", "\\normalsize \n\n")
  } else if (stringr::str_ends(path, "(htm|html)")) {
    if(Sys.which("wkhtmltopdf") != "") {
      cat("## ", basename(path), "\n\n", "Content of HTML file (starts on next page):", "\n\n")
      out_file <- paste0(path, ".pdf")
      system2("wkhtmltopdf", c(shQuote(path), shQuote(out_file)))
      cat(paste0("\\includepdf[pages={-}]{", out_file, "}"))
      cat("\n\n End of ", basename(path), "on previous page.", "\n\n")
    } else {
      cat("## ", basename(path), "\n\n")
      cat("Cannot inlcude output file as figure.")
    }
  } else {
    cat("## ", basename(path), "\n\n")
    cat("Cannot inlcude output file as figure.")
  }
  
  cat("\\clearpage \n\n")
}
```

<!--
## Acknowledgements

I would like to thank Dr Bhatt and his team for promptly answering any
queries I had with this reproduction.  CODECHECK is financially
supported by the Mozilla foundation.
-->

# Citing this document

```{r, results='asis',echo=FALSE}
cite_certificate(metadata)
```

# About CODECHECK

This certificate confirms that the codechecker could independently
reproduce the results of a computational analysis given the data and
code from a third party.  A CODECHECK does not check whether the
original computation analysis is correct.  However, as all materials
required for the reproduction are freely available by following the
links in this document, the reader can then study for themselves the
code and data.


# About this document

This document was created using [R Markdown](https://rmarkdown.rstudio.com/) using the [`codecheck`](https://github.com/codecheckers/codecheck) R package.
`make codecheck.pdf` will regenerate the report file.

```{r}
sessionInfo()
```

```{r, include=FALSE, eval=FALSE}
# render this document in RStudio
rmarkdown::render("codecheck.Rmd", output_format = "pdf_document") 
```
